Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-11 ms.tex
Make minor changes to Introduction
From 758a6e2:
============

In ms.tex,

(*) Make minor changes to Introduction

Sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} are yet to become operational. In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA), currently under construction, will be much closer in its capability to detect and place definitive constraints on the reionization epoch relative to the SKA and far ahead of current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.

@@

>>>>

Sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} are yet to become operational. In the meanwhile, the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA), currently under development, will be much more advanced in its capability to detect and place definitive constraints on the reionization epoch relative to current instruments such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, and the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, which have only enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14}.

@@

% \begin{thebibliography}{}
% \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

% \bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
% {Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166

% \bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
%   {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
%   {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
%   {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
%   {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
%   {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
%   {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
%   {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
%   \& {Wyithe}}]{bea13}
% {Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
%   429, L5

% \bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
%   {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
% {Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
%   500, 965

% \bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
%   {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
%   {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
% {Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67

% \bibitem[{{Bowman} {et~al.}(2006){Bowman}, {Morales}, \& {Hewitt}}]{bow06}
% {Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2006, \apj, 638, 20

% \bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
% ---. 2009, \apj, 695, 183

% \bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
%   {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
%   {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
%   {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
%   {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
%   {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
%   {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
%   {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
%   {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
%   {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
%   {Wyithe}}]{bow13}
% {Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31

% \bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
% {Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526

% \bibitem[{{Di Matteo} {et~al.}(2004){Di Matteo}, {Ciardi}, \&
%   {Miniati}}]{dim04}
% {Di Matteo}, T., {Ciardi}, B., \& {Miniati}, F. 2004, \mnras, 355, 1053

% \bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
%   {Rees}}]{dim02}
% {Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576

% \bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
% Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005

% \bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
%   {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
%   {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
%   {Webster}}]{dil14}
% {Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002

% \bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04}
% {Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039

% \bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
% {Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181

% \bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
%   {Chengalur}}]{gho12}
% {Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
%   2012, \mnras, 426, 3295

% \bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
% {Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383

% \bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
%   {Martel}}]{ili02}
% {Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
%   572, L123

% \bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
%   {Trott}}]{liu14a}
% {Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
%   023018

% \bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
%   {Trott}}]{liu14b}
% ---. 2014{\natexlab{b}}, \prd, 90, 023019

% \bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
% {Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006

% \bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
%   {Zaldarriaga}}]{liu09}
% {Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
%   2009, \mnras, 398, 401

% \bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
%   {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
%   {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
%   {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
%   {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
%   {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
%   {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
%   {Whitney}, {Williams}, \& {Williams}}]{lon09}
% {Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
%   Proceedings, 97, 1497

% \bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
% {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429

% \bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
%   {Hernquist}, \& {Furlanetto}}]{mcq06}
% {McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
%   S.~R. 2006, \apj, 653, 815

% \bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
% {Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767

% \bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
%   {Beardsley}}]{mor12}
% {Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
%   \apj, 752, 137

% \bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
% {Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7

% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
%   {Jacobs}, \& {Aguirre}}]{par12a}
% {Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
%   2012{\natexlab{a}}, \apj, 753, 81

% \bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
%   {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
% {Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
%   2012{\natexlab{b}}, \apj, 756, 165

% \bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
%   {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
%   {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
% {Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
%   1468

% \bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
%   {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
%   {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
% {Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
%   L36

% \bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
%   {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
%   {Parsons}, {Tegmark}, \& {Werthimer}}]{pob14}
% {Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66

% \bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
% {Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575

% \bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
% {Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510

% \bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
% {Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189

% \bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
% {Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
%   {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)

% \bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
%   {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
%   {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
%   {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
%   {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
%   {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
%   {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
%   {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
%   {Williams}, \& {Wyithe}}]{thy13}
% {Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
%   \apj, 776, 6

% \bibitem[{{Thyagarajan} {et~al.}(2015){Thyagarajan}, {Jacobs}, {Bowman},
%   {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll}, {Corey},
%   {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng}, {Goeke},
%   {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker}, {Johnston-Hollitt},
%   {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg}, {Lenc}, {Line},
%   {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter}, {Mitchell}, {Morales},
%   {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober},
%   {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi}, {Udaya Shankar}, {Sethi},
%   {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark}, {Tingay}, {Trott},
%   {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, {Williams}, {Wu}, \&
%   {Wyithe}}]{thy15}
% {Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.} 2015, ArXiv
%   e-prints, arXiv:1502.07596

% \bibitem[{{Tingay} {et~al.}(2013){Tingay}, {Goeke}, {Bowman}, {Emrich}, {Ord},
%   {Mitchell}, {Morales}, {Booler}, {Crosse}, {Wayth}, {Lonsdale}, {Tremblay},
%   {Pallot}, {Colegate}, {Wicenec}, {Kudryavtseva}, {Arcus}, {Barnes},
%   {Bernardi}, {Briggs}, {Burns}, {Bunton}, {Cappallo}, {Corey}, {Deshpande},
%   {Desouza}, {Gaensler}, {Greenhill}, {Hall}, {Hazelton}, {Herne}, {Hewitt},
%   {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg},
%   {Lynch}, {Mckinley}, {Mcwhirter}, {Morgan}, {Oberoi}, {Pathikulangara},
%   {Prabu}, {Remillard}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Udaya-Shankar},
%   {Schlagenhaufer}, {Srivani}, {Stevens}, {Subrahmanyan}, {Waterson},
%   {Webster}, {Whitney}, {Williams}, {Williams}, \& {Wyithe}}]{tin13}
% {Tingay}, S.~J., {Goeke}, R., {Bowman}, J.~D., {et~al.} 2013, \pasa, 30, 7

% \bibitem[{{Tozzi} {et~al.}(2000){Tozzi}, {Madau}, {Meiksin}, \& {Rees}}]{toz00}
% {Tozzi}, P., {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 2000, \apj, 528, 597

% \bibitem[{{Trott} {et~al.}(2012){Trott}, {Wayth}, \& {Tingay}}]{tro12}
% {Trott}, C.~M., {Wayth}, R.~B., \& {Tingay}, S.~J. 2012, \apj, 757, 101

% \bibitem[{{van Cittert}(1934)}]{van34}
% {van Cittert}, P.~H. 1934, Physica, 1, 201

% \bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
%   {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
%   {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
%   {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
%   {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
%   {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
%   Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^i}rzan}, {Bonafede},
%   {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
%   {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
%   {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
%   {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
%   {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
%   {Garrett}, {de Gasparin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
%   {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
%   Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
%   {Jelic}, {de Jong}, {Kant}, {Karastergiou}, {Koers}, {Kollen}, {Kondratiev},
%   {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer}, {Kuper},
%   {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat}, {Macario},
%   {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering}, {Meulman},
%   {Mevius}, {Millenaar}, {Miller-Jones}, {Mohan}, {Mol}, {Morawietz},
%   {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis}, {van Nieuwpoort},
%   {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson}, {Omar}, {Orr{\'u}},
%   {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo}, {Polatidis},
%   {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma}, {Renting},
%   {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van der Schaaf},
%   {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek}, {Serylak},
%   {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz}, {Sterks},
%   {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas}, {Thoudam},
%   {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen}, {ter Veen},
%   {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos}, {van der Wal},
%   {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds}, {Wilhelmsson},
%   {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van Zwieten}}]{van13}
% {van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
%   A2

% \bibitem[{{Wang} {et~al.}(2006){Wang}, {Tegmark}, {Santos}, \& {Knox}}]{wan06}
% {Wang}, X., {Tegmark}, M., {Santos}, M.~G., \& {Knox}, L. 2006, \apj, 650, 529

% \bibitem[{{Zaldarriaga} {et~al.}(2004){Zaldarriaga}, {Furlanetto}, \&
%   {Hernquist}}]{zal04}
% {Zaldarriaga}, M., {Furlanetto}, S.~R., \& {Hernquist}, L. 2004, \apj, 608, 622

% \bibitem[{{Zernike}(1938)}]{zer38}
% {Zernike}, F. 1938, Physica, 5, 785

% \end{thebibliography}
